Supporting Information

### 2015-10-23 si.Rmd
SI decrufted. Table of references for in situ comp figure (fixes #2)

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage{caption}
  \usepackage{fixltx2e}
  \usepackage{lscape}
  \usepackage{rotating}
  \captionsetup[figure]{labelfont=bf}
  \renewcommand{\thefigure}{S\arabic{figure}}
  \renewcommand{\tablename}{ \hfill \newline Table}
  \renewcommand{\thetable}{S\arabic{table}}
documentclass: tufte-handout
classoption: a4paper
output:
  rmarkdown::tufte_handout:
    dev: CairoPDF
    keep_tex: yes
  BiocStyle::html_document:
    dev: CairoPDF
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
bibliography: bib/papersLib.bibtex
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               fig.align = 'center', 
#               dev=c("png", "cairo_pdf"),
               dpi=300,
               fig.show='hold',
               fig.height = 4.213,
               fig.width = 4.213,
               crop = FALSE,
#               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

#pander::panderOptions("table.caption.prefix", "")
source('src/R/figures.R')

``` {r st_libStats, results = "hide", fig.cap = I(pasteLabel("**Table S", s_tableCount, "st_libStats"))}

pander::set.caption(paste0(
  I(pasteLabel("**Table S", s_tableCount, "st_libStats")),
  "**: Library and sequencing statistics."))
pander::pandoc.table(st_libStats,
                     missing = "",
                     round = 1,
                     emphasize.strong.cols = 1,
                     split.tables = Inf,
                     justify = c("right", rep("center", length(names(st_libStats)) - 1)))

@@

``` {r st_libstats2, results = "asis"}

st_libStats_x <- as.data.frame(st_libStats)
rownames(st_libStats_x) <- st_libStats_x$Library
st_libStats_x$Library <- NULL
st_libStats_x <- xtable::xtable(st_libStats_x)
xtable::digits(st_libStats_x) <- c(0, rep(1, ncol(st_libStats_x) - 1), 0)
#xtable::caption(st_libStats_x) <- "Library and sequencing statistics."

@@

cat(st_libStats_x_print)

#cat(sub("\\begin{table*}[ht]\n", "\\begin{table*}[ht]\n\\caption{Library and sequencing statistics.} \n", st_libStats_x_print, fixed = TRUE))

@@

```{r st_reviewInSitu, results = "hide"}
pander::set.caption(paste0(
  I(pasteLabel("**Table S", s_tableCount, "st_reviewInSitu")),
  "**: Comparison of the dataset with published *in situ* expression profiles. '×' indicates that the gene was detected by both methods, '+' indicates that the gene was detected by *in situ* hybridisation but not by RNA sequencing and '·' indicates that the gene was detected by RNA sequencing but expression was not reported by *in situ*. The last category is not intended to be informative, because it relies on negative or unreported results. A blank cell indicates that the gene was not detected by either method."))
pander::pandoc.table(st_reviewInSitu, split.tables = Inf,
                     justify = c("right", rep("centre", length(names(st_reviewInSitu)) - 2), "left"),
                     emphasize.cols = c(1,2), missing = "")
```

@@

```{r sf_isGenesTpm, fig.height = 9.535, fig.cap = paste0("\\protect\\label{fig:sf_isGenesTpm}","Comparison of the LMD RNA-sequencing dataset with published \\emph{in situ} results. Expression value in transcripts per million (TPM) is shown on the \\emph{y}-axis, and points are plotted as a triangle if the expression value was above the cutoff for that library or a circle if below. Grey shading indicates a meristem type for which expression was detected by \\emph{in situ} hybridisation. See Table \\ref{tab:refFrame_x} for references for the \\emph{in situ} expression patterns. [\\textbf{As this is now detable-ized include a separate supplemantary table of references}] Although four replicates were produced from each of the RM and PBM, only three replicates for each stage are included in the analysis (see Results).")}

print(sf_isGenesTpm)

@@

```{r insituRefs, results = "asis"}

# refFrame_x <- print(xtable::xtable(refFrame,
#                                    caption = "References for Figure \\ref{fig:sf_isGenesTpm}",
#                                    label = "tab:refFrame_x"),
#       type = "latex",
#       floating = TRUE,
#       floating.environment = "table",
#       rotate.colnames = FALSE,
#       print.results = FALSE)

setnames(refTable, c("msuId", "plotLabel"), c("MSU name", "CSGNL symbol"))
pander::set.caption("\\protect\\label{tab:refFrame_x}References for Figure \\ref{fig:sf_isGenesTpm}.")
pander::pandoc.table(refTable, emphasize.cols = c(1,2))
```

@@

```{r sf_mfuzzCentroids, fig.cap = paste0("Minimum centroid distance for 2–", maxClust, " cluster cores (\\emph{c}). Eight cluster cores were indicated because the rate of change of the minimum centroid distance over \\emph{c} decreases after \\emph{c} = 8."), fig.scap = "Something", fig.scap = c("One plot", "Another plot")}

print(sf_mfuzzCentroids)

@@

```{r sf_madsTree, fig.height = 9.535, fig.cap = paste0("Differential expression of putatative MIKC proteins in \\emph{A. thaliana}, \\emph{Solanum lycopersicum} and \\emph{Oryza sativa} ssp. \\emph{japonica}. The tree is a neighbour-joining tree estimated from genetic distance of amino acid sequences. Named proteins starting with AT\\_ or OS\\_ are from Arabidopsis or rice respectively, with synonyms in parentheses, and other proteins are labelled with their unique identifiers.", "\\newline ", "The colour of the label represents the Log\\textsubscript{2}-fold change (L\\textsubscript{2}FC) in expression of the gene encoding that protein between undifferentiated and differentiated meristems. Where there is no coloured label, the adjusted \\emph{p}-value associated with the difference in expression was greater than 0.1, or the gene for the protein in question was excluded from the differential expression analysis by `DESeq2`, which may occur because of low read counts, an extreme count outlier or the gene failing independent filtering \\citep{@Love:2014do}.", "\\newline ", "For rice, L\\textsubscript{2}FC was estimated from the RM and SM samples reported here. For \\emph{A. thaliana}, L\\textsubscript{2}FC was estimated using the inflorescence meristem and floret meristem samples reported by \\citep{Mantegazza:2014di}. The sympodial inflorescence meristem and floret meristem samples generated by \\citep{Park:2012dg} were used to estimate L\\textsubscript{2}FC values for tomato genes. Clades are labelled following the nomenclature presented by \\citep{Arora:2007fa}.")}

print(sf_madsTree)
```

>>>>

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage{caption}
  \usepackage{fixltx2e}
  \usepackage{rotating}
  \renewcommand{\thefigure}{S\arabic{figure}}
  \renewcommand{\thetable}{S\arabic{table}}
documentclass: tufte-handout
classoption: a4paper
output:
  rmarkdown::tufte_handout:
    dev: CairoPDF
    keep_tex: yes
bibliography: bib/papersLib.bibtex
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               fig.align = 'center', 
               dpi=600,
               fig.show='hold',
               fig.height = 4.213,
               fig.width = 4.213,
               crop = FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

source('src/R/figures.R')

@@

``` {r st_libstats, results = "asis"}
st_libStats_x <- as.data.frame(st_libStats)
rownames(st_libStats_x) <- st_libStats_x$Library
st_libStats_x$Library <- NULL
st_libStats_x <- xtable::xtable(st_libStats_x)
xtable::digits(st_libStats_x) <- c(0, rep(1, ncol(st_libStats_x) - 1), 0)

@@

cat(st_libStats_x_print)
```

@@

@@

```{r sf_isGenesTpm, fig.height = 9.535, fig.cap = paste0("\\protect\\label{fig:sf_isGenesTpm}","Comparison of the LMD RNA-sequencing dataset with published \\emph{in situ} results. Expression value in transcripts per million (TPM) is shown on the \\emph{y}-axis, and points are plotted as a triangle if the expression value was above the cutoff for that library or a circle if below. Grey shading indicates a meristem type for which expression was detected by \\emph{in situ} hybridisation. See Table \\ref{tab:refFrame_x} for references for the \\emph{in situ} expression patterns. [\\textbf{As this is now detable-ized include a separate supplemantary table of references}] Although four replicates were produced from each of the RM and PBM, only three replicates for each stage are included in the analysis (see Results).")}
print(sf_isGenesTpm)
```

@@

```{r insituRefs, results = "asis"}
setnames(refTable, c("msuId", "plotLabel"), c("MSU name", "CSGNL symbol"))
pander::set.caption("\\protect\\label{tab:refFrame_x}References for Figure \\ref{fig:sf_isGenesTpm}.")
pander::pandoc.table(refTable, emphasize.cols = c(1,2))
```

@@

```{r sf_mfuzzCentroids, fig.cap = paste0("Minimum centroid distance for 2–", maxClust, " cluster cores (\\emph{c}). Eight cluster cores were indicated because the rate of change of the minimum centroid distance over \\emph{c} decreases after \\emph{c} = 8."), fig.scap = "Something", fig.scap = c("One plot", "Another plot")}
print(sf_mfuzzCentroids)
```

@@

```{r sf_madsTree, fig.height = 9.535, fig.cap = paste0("Differential expression of putatative MIKC proteins in \\emph{A. thaliana}, \\emph{Solanum lycopersicum} and \\emph{Oryza sativa} ssp. \\emph{japonica}. The tree is a neighbour-joining tree estimated from genetic distance of amino acid sequences. Named proteins starting with AT\\_ or OS\\_ are from Arabidopsis or rice respectively, with synonyms in parentheses, and other proteins are labelled with their unique identifiers.", "\\newline ", "The colour of the label represents the Log\\textsubscript{2}-fold change (L\\textsubscript{2}FC) in expression of the gene encoding that protein between undifferentiated and differentiated meristems. Where there is no coloured label, the adjusted \\emph{p}-value associated with the difference in expression was greater than 0.1, or the gene for the protein in question was excluded from the differential expression analysis by `DESeq2`, which may occur because of low read counts, an extreme count outlier or the gene failing independent filtering \\citep{@Love:2014do}.", "\\newline ", "For rice, L\\textsubscript{2}FC was estimated from the RM and SM samples reported here. For \\emph{A. thaliana}, L\\textsubscript{2}FC was estimated using the inflorescence meristem and floret meristem samples reported by \\citep{Mantegazza:2014di}. The sympodial inflorescence meristem and floret meristem samples generated by \\citep{Park:2012dg} were used to estimate L\\textsubscript{2}FC values for tomato genes. Clades are labelled following the nomenclature presented by \\citep{Arora:2007fa}.")}
print(sf_madsTree)
```
